Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-02-25 tpe_edreview_rebuttal.txt

> 
> The paper raises a few questions in this reviewer's mind, and in
> elsewhere it offers opportunities for suggestions.
> 
> 1.  Question.  First paragraph in "Introduction": The third sentence
> "Here I interpret straight line as the path adopted by a stationary,
> light inextensible string under tension passing between two points."
> Is this to be understood as identical to the definition of "geodesic"?
> If that is the assumption, can it be justified, because when one
> thinks of geodesic in General Relativity, one has "free-fall" in mind,
> and the stretched string, being "stationary," would not be in
> free-fall in the global coordinate system.

I think the sentence in question was technically correct but
potentially misleading.  What I wanted to do was to make readers think
about taut thread in the context of GR.  I didn't want to consider
geodesics at this point in the introduction, or free-falling elevator
frames.  I want to focus on taut string.

[one of the conceptual difficulties in preparing the manuscript, as
pointed out by a previous reviewer, is that the string is not in a
freely-falling elevator frame; as the reviewer points out, such string
does not follow a geodesic path in any meaningful sense].

I have rephrased the sentence which now reads: "Here I consider the
path adopted by a stationary, light inexensible string under tension
passing between two fixed points, and consider the extent to which the
expression "straight line" would be applicable to such an object".

### 2021-02-25 string_physics_educator_revision3.tex
the points are fixed (issue #34)

General relativity is a topic of long-standing fascination for physics
undergraduates~\cite{christensen2012,taylor2000}.  Students appreciate
everyday illustrations of the concepts involved, as recent educational
work on gravitational wave visualisations attests~\cite{overduin2018}.
Here I consider the path adopted by a stationary,
light inexensible string under tension passing between two points, and consider the extent to which the expression  ``straight line'' would be applicable to such an object.
The analysis presented here would be suitable for an undergraduate
homework problem~\cite{romano2019}.

>>>>

General relativity is a topic of long-standing fascination for physics
undergraduates~\cite{christensen2012,taylor2000}.  Students appreciate
everyday illustrations of the concepts involved, as recent educational
work on gravitational wave visualisations attests~\cite{overduin2018}.
Here I consider the path adopted by a stationary,
light inexensible string under tension passing between two fixed points, and consider the extent to which the expression  ``straight line'' would be applicable to such an object.
The analysis presented here would be suitable for an undergraduate
homework problem~\cite{romano2019}.
